---
title       : Body Mass Index and Percent Fat Calculator
subtitle    : BMI and %Fat and Classification
author      : AKW
job         : EE
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

### About Body Mass Index and Percent Fat Calculator

This application is developed to calculate:

1. Body Mass Index (BMI)
2. Percent fat Content

The weight classification is determined using the calcutaed BMI value as:

1. Underweight (BMI<18.5)
2. Normal Wight (18.5<BMI<24.9)
3. Overweight (24.9<BMI<29.9) or
4. Obese (BMI>30)

--- .class #id 

### Body Mass Index Calculations

The Body Mass Index (BMI) is calculated as:

#### $$BMI=\frac{weight*730} {height^2}$$

where;  weight is body weight in pounds and
        height is body height in inches      
source: http://www.scientificpsychic.com/fitness/diet.html

```{r echo=TRUE}
weight<-100 ## initial value for weight
height <- 70 ## initial value for height
BMI<- (weight*703)/(height^2)
BMI
```

--- .class #id 

### Percent Fat Calculations

The Percent fat content is determined based on the BMI, age, and gender:
The Percent fat conten is estimated using the following equations:

For adults (age >15 years) and Adults (age >15 years):


#### $Child Body Fat =(1.51*BMI)-(0.70*Age)-(3.6*gender)+1.4$

#### $Adult Body Fat =(1.20*BMI)+(0.23*Age)-(10.8*gender)-5.4$


```{r echo=TRUE}
weight<-100; height <- 70; agec <-15; agea <-25; gender<-0 

PercentFatChildren=(1.51*(weight*703)/(height^2)) - (0.70*agec) - (3.6*gender) + 1.4
PercentFatAdult=(1.20*(weight*703)/(height^2)) + (0.23*agea) - (10.8*gender) - 5.4
PercentFatChildren;  PercentFatAdult

```

---

### Application

Knowing Body Mass Index (BMI) and Percent Fat is very essential to 
monitor one's helath status

This Application (BMI_Calc)can be used to calculate BMI and % fat 
content from radiliy available measurments of body weight and body 
height as well as age and gender of the person.
